Bearing Fault Diagnosis Based on Deep Belief Network

### 2019-06-10 Paper/main.tex
no message

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{dbnVSbp.eps}
	\caption{Comparison of classification accuracy between traditional back propagation neural network and DBN in 1000 epoches.}
	\label{fig:dbnVSbp}
\end{figure}

@@

\subsection{DBN and SSDBN}
\textcolor{red}{Finally, we compare DBN with SSDBN. Since SSDBN has studied the sample labels at RBM, I thought that the initial classification accuracy rate should be higher than DBN, but the result is not the case. However, the final classification accuracy rate of SSDBN is higher than DBN.}

>>>>

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\columnwidth]{dbnVSbp.eps}
	\caption{Comparison of classification accuracy between traditional back propagation neural network and DBN in 1500 epoches.}
	\label{fig:dbnVSbp}
\end{figure}

@@

\subsection{DBN and SSDBN}
\textcolor{red}{Finally, we compare DBN with SSDBN. Since SSDBN has studied the sample labels at RBM, I thought that the initial classification accuracy rate should be higher than DBN, but the result is not the case. However, SSDBN converges faster and the final classification accuracy rate of SSDBN is higher than DBN.}
